Evolving Robot Gaits in Hardware: the HyperNEAT Generative Encoding Vs. Parameter Optimization

### 2011-06-13 paper_ecal/learningMethods.tex
few small tweaks, and the necessary shortening elsewhere to keep them space neutral

\emph{Nelder-Mead simplex method}: The Nelder-Mead simplex
  method creates an initial simplex with $d+1$ vertices,
  for a $d$ dimensional parameter space. It then tests the
  fitness of each vertex, and, in general, it reflects the worst point
  over the simplex's centroid in an attempt to improve it.  Several additional
  rules are used to prevent cycles and local minima; see \cite{nm} for more information.

>>>>

\emph{Nelder-Mead simplex method}: The Nelder-Mead simplex
  method creates an initial simplex with $d+1$ vertices
  for a $d$ dimensional parameter space. It then tests the
  fitness of each vertex and, in general, it reflects the worst point
  over the simplex's centroid in an attempt to improve it.  Several additional
  rules are used to prevent cycles and local minima; see \cite{nm} for more information.
